Characterization and Photometric Performance of the Hyper Suprime-Cam Software Pipeline.

### 2017-04-30 draft/ms_v5.tex
New figure and table caption

\newcommand{\plus}{\raisebox{.4\height}{\scalebox{.6}{+}}}
\newcommand{\minus}{\raisebox{.4\height}{\scalebox{.8}{-}}}
\newcommand{\smag}{$\sigma_{\Delta\mathrm{mag}}$}
\newcommand{\mmag}{$\left<{\Delta\mathrm{mag}}\right>$}
\newcommand{\n}{$\minus$}

@@

@@

%% ------------------------------------------------------------------------------------ %%
%% Fig: Star Sample
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_star_sample}
    \end{center}
    \caption{
        Magnitude and color distributions of synthetic stars.
        \textbf{Upper panel}: five-band magnitude distributions of the COSMOS
        stars (filled histograms) and  resampled stars (dashed lines).
        \textbf{Lower panel}: color-color distributions
        (left: $g-r$ v.s. $r-i$; right: $i-z$ v.s. $z-y$). 
        Hexagonal bins indicate COSMOS stars and contours indicate resampled stars.
        }
    \label{fig:star_sample}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %%
%% Fig: Magnitude v.s S/N for stars
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_psf_sn}
    \end{center}
    \caption{
        Relation between input magnitudes (\textbf{left}: $i$-band; \textbf{right}:
        $g$-band) of synthetic stars and the $\log (\mathrm{S}/\mathrm{N})$ measured 
        by \hscpipe{} PSF photometry.
        Hexagonal binned density plots and contours show the distributions for
        stars in both the \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}. 
        Highly blended stars are highlighted using scatter plots.
        The gray dashed line marks $S/N = 5$ which is the detection threshold used 
        by \hscpipe{}.  
        Our 5$\sigma$ point source detection limit is ${\sim}26.5$ mag in $i$-band,
        however we do not reach these magnitudes with our current synthetic stellar 
        input catalog.
        }
    \label{fig:star_sn}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
%% Fig: Accuracy of Forced PSF Magnitudes
\begin{figure*}
    \begin{center}
        \includegraphics[width=16cm]{fig/synpipe_psf_mag}
    \end{center}
    \caption{
        Accuracy of the \texttt{hscpipe} PSF photometry for synthetic stars measured
        by the difference between input and output \forced{} PSF magnitudes.
        Plots [a, b, c, d, e] show the results for [$g$, $r$, $i$, $z$, $y$]-band, 
        respectively.
        The left panel in each plot shows the relation between input magnitude and
        magnitude difference.
        Hexagonal binned density plots and contours are for the synthetic galaxies 
        from \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}.
        Highly blended objects are highlighted using scattered points.
        The long-dashed lines mark zero magnitude difference, while the pairs of
        dashed lines outline the running-median of PSF magnitude errors
        (including the uncertainties in aperture correction).
        The right panel in each plot shows the distributions of the magnitude 
        differences for objects in \texttt{goodSeeing} (filled) and \texttt{badSeeing}
        (solid line) \tracts{}.
        The dashed lines identify the distribution of highly blended objects.
        }
    \label{fig:psf_mag}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %%
%% Fig: Astrometric Calibration
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_astrometry}
    \end{center}
    \caption{
        Astrometric accuracy for synthetic stars (\textbf{left}) and galaxies
        (\textbf{right}). 
        We show the differences between the input R.A and Dec and the coordinates 
        measured on the \coadd{} images. 
        Hexagonal bins (filled histogram) and contours (solid-line histogram) are 
        for synthetic objects from \tracts{} with good and bad seeing conditions, 
        respectively.
        $\Delta\mathrm{R.A}=0$ and $\Delta\mathrm{Dec}=0$ are marked by dashed lines.     
        It shows that the initial astrometric calibration is already very accurate,  
        and it also suggests that \hscpipe{} can find the centroids of stars and 
        galaxies with precisions that are consistent with the astrometric calibration
        uncertainty under moderately different seeing conditions.
        }
    \label{fig:astrometry}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
%% Fig: Star-Galaxy Separation
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_star_galaxy}
    \end{center}
    \caption{Evaluation of the \hscpipe{} star--galaxy separation scheme. 
        Star--galaxy separation is based on the the magnitude difference between the 
        PSF and \cmodel{} photometry. 
        The plot on the \textbf{left} (a) corresponds to synthetic stars. 
        Hexagonal bins and filled histogram show distributions of correctly classified
        synthetic stars in the \texttt{goodSeeing} \tract{}.
        The scatter plot (dashed-line histogram) and contour (solid-line histogram)
        show distributions of synthetic stars that are misclassified as extended
        objects in \tracts{} with bad and good seeing conditions, respectively.
        The plot on the \textbf{right} (b) corresponds to synthetic galaxies.
        Hexagonal bins (filled histogram) and contours (solid-line histogram)
        are for galaxies from \texttt{goodSeeing} and \texttt{badSeeing} \tracts{},
        respectively.
        The scatter plot and dashed-line histogram highlight synthetic galaxies that 
        are misclassified as point sources.}
    \label{fig:sg}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
%% Fig: Relations between Blendedness and Photomertic Errors
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_blendedness_err}
    \end{center}
    \caption{
        Relation between the $\log_{10} (\mathrm{Blendedness})$ parameter
        and the photometric accuracy f synthetic stars (\textbf{upper row}, a and 
        b) and galaxies (\textbf{lower row}, c and d).
        \textbf{Left} columns (a and c) show the uncertainties in PSF and/or \cmodel{} 
        magnitudes. \textbf{Right} columns (b and d) show the uncertainties in 
        $(g-i)$ colors.
        Hexagonal bins and contours show results for \texttt{goodSeeing} and
        \texttt{badSeeing} \tracts{}, respectively.
        $\log_{10} (\mathrm{Blendedness}) = -1.0$ is marked using a vertical dashed 
        line.
        }
    \label{fig:blend}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
%% Fig: HSC cModel has problem recovering the size and shape of galaxies
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_galaxy_ba}
    \end{center}
    \caption{
        Accuracy of weighted axis ratio estimates for synthetic
        galaxies using \cmodel{} photometry.
        The \textbf{left} (a) plot shows the relation between the input $(b/a)$ and 
        the uncertainty in $(b/a)$.
        The \textbf{right} (b) plot shows the relation between input magnitude and 
        the undertainty in $(b/a)$.
        Contours are for the default test with \texttt{usePixelWeights=False}, and 
        hexagonal bins correspond to \texttt{usePixelWeights=True}.
        }
    \label{fig:galaxy_ba}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %%
% Table 1 : Magnitudes for PSF
\begin{table*}
    \begin{center}
    %% -------------------------------------------------------------------------------- %%
    \begin{tabular}{| c | c | c | ccccccc |}
    \hline
    Filter &   Seeing    &  Statistics & \multicolumn{7}{|c|}{Input Magnitudes (mag)} \\
    \cline{4-10}
           & FWHM ($$\asec) &             & 19.0 & 20.0 & 21.0 & 22.0 & 23.0 & 24.0 & 25.0 \\
    \hline
    $g$ & 0.45 & \smag{} & 0.016 & 0.017 & 0.019 & 0.023 & 0.029 & 0.043 & 0.078 \\
        &      & \mmag{}  & 0.008 & 0.009 & 0.009 & 0.009 & 0.008 & 0.007 & $\minus 0.003$ \\
        \cline{3-10}
        & 0.70 & \smag{} & 0.016 & 0.018 & 0.019 & 0.021 & 0.026 & 0.039 & 0.091 \\
        &      & \mmag{}  & 0.007 & 0.006 & 0.006 & 0.005 & 0.004 & 0.003 & $\minus 0.002$ \\
    \hline
    $r$ & 0.45 & \smag{} & 0.021 & 0.023 & 0.024 & 0.025 & 0.027 & 0.035 & 0.064 \\
        &      & \mmag{}  & 0.011 & 0.011 & 0.012 & 0.011 & 0.012 & 0.011 & 0.011 \\
        \cline{3-10}
        & 0.70 & \smag{} & 0.026 & 0.029 & 0.031 & 0.034 & 0.041 & 0.054 & 0.090 \\
        &      & \mmag{}  & 0.009 & 0.009 & 0.009 & 0.009 & 0.009 & 0.006 & 0.001 \\    
    \hline
    $i$ & 0.45 & \smag{} & 0.015 & 0.015 & 0.017 & 0.018 & 0.020 & 0.030 & 0.047 \\
        &      & \mmag{}  & 0.002 & 0.002 & 0.002 & 0.002 & 0.002 & 0.002 & 0.003 \\
        \cline{3-10}
        & 0.70 & \smag{} & 0.012 & 0.013 & 0.014 & 0.016 & 0.022 & 0.043 & 0.050 \\
        &      & \mmag{}  & 0.001 & 0.002 & 0.002 & 0.002 & 0.002 & 0.001 & $\minus 0.012$ \\    
    \hline
    $z$ & 0.45 & \smag{} & 0.011 & 0.013 & 0.014 & 0.016 & 0.025 & 0.053 & 0.094 \\
        &      & \mmag{}  & 0.002 & 0.002 & 0.002 & 0.003 & 0.003 & 0.005 & $\minus 0.001$ \\
        \cline{3-10}
        & 0.70 & \smag{} & 0.019 & 0.020 & 0.021 & 0.024 & 0.038 & 0.071 & 0.104 \\
        &      & \mmag{}  & 0.003 & 0.003 & 0.003 & 0.004 & 0.005 & 0.003 & $\minus 0.010$ \\    
    \hline
    $y$ & 0.45 & \smag{} & 0.017 & 0.017 & 0.021 & 0.033 & 0.074 & 0.138 & -- \\
        &      & \mmag{}  & 0.006 & 0.006 & 0.006 & 0.006 & 0.000 & $\minus 0.001$ & -- \\
        \cline{3-10}
        & 0.70 & \smag{} & 0.019 & 0.019 & 0.023 & 0.037 & 0.077 & 0.153 & -- \\
        &      & \mmag{}  & 0.007 & 0.008 & 0.008 & 0.006 & 0.003 & $\minus 0.034$ & -- \\    
    \hline  
    \end{tabular}
    %% -------------------------------------------------------------------------------- %%
    \end{center}
    \caption{
        \todo{Placeholder}
        Summary of the \smag{}s and accuracies of \forced{} PSF magnitudes in all 
        five bands and in both \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}.  
    }
        \label{tab:psfmag}
\end{table*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
% Table 2 : PSF Color
\begin{table*}
    \begin{center}
    %% -------------------------------------------------------------------------------- %%
    \begin{tabular}{| c | c | c | ccccccc |}
    \hline
    Filter &   Seeing       &  Statistics & \multicolumn{4}{|c|}{Input $i$ band Magnitudes (mag)} \\
    \cline{4-10}
           & FWHM ($$\asec) &             & 19.0 & 20.0 & 21.0 & 22.0 & 23.0 & 24.0 & 25.0 \\
    \hline
    $(g-i)$ & 0.45 & \smag{} & 0.023 & 0.026 & 0.037 & 0.054 & 0.077 & 0.105 & 0.117 \\
            &      & \mmag{}  & 0.008 & 0.007 & 0.005 & 0.003 & $\minus 0.002$ & $\minus 0.009$ & $\minus 0.035$ \\
            \cline{3-10}
            & 0.70 & \smag{} & 0.021 & 0.025 & 0.033 & 0.051 & 0.075 & 0.105 & 0.137 \\
            &      & \mmag{}  & 0.004 & 0.003 & 0.002 & 0.001 & $\minus 0.001$ & $\minus 0.002$ & 0.007 \\
    \hline
    $(i-y)$ & 0.45 & \smag{} & 0.019 & 0.020 & 0.022 & 0.031 & 0.058 & 0.109 & 0.189 \\
            &      & \mmag{}  & $\minus 0.004$ & $\minus 0.004$ & $\minus 0.004$ & $\minus 0.004$ & $\minus 0.002$ & 0.011 & 0.064 \\
            \cline{3-10}
            & 0.70 & \smag{} & 0.019 & 0.020 & 0.021 & 0.031 & 0.057 & 0.123 & 0.221 \\
            &      & \mmag{}  & $\minus 0.006$ & $\minus 0.006$ & $\minus 0.006$ & $\minus 0.005$ & $\minus 0.005$ & $\minus 0.002$ & $\minus 0.064$ \\    
    \hline  
    \end{tabular}
    %% -------------------------------------------------------------------------------- %%
    \end{center}
    \caption{
        \todo{Placeholder}
        Summary of the \smag{}s and accuracies of \forced{} PSF colors in both 
        \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}.  
        We show results for both $(g-i)$ and $(i-y)$ PSF colors.
    }
        \label{tab:psfcolor}
\end{table*}
%% ------------------------------------------------------------------------------------ %%

>>>>

\newcommand{\plus}{\raisebox{.4\height}{\scalebox{.6}{+}}}
\newcommand{\minus}{\raisebox{.4\height}{\scalebox{.8}{-}}}
\newcommand{\smag}{$\sigma_{\Delta\mathrm{Mag}}$}
\newcommand{\mmag}{$\left<{\Delta\mathrm{Mag}}\right>$}
\newcommand{\scolor}{$\sigma_{\Delta\mathrm{Color}}$}
\newcommand{\mcolor}{$\left<{\Delta\mathrm{Color}}\right>$}
\newcommand{\n}{$\minus$}

@@

%% ------------------------------------------------------------------------------------ %%
%% Fig: Star Sample
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_star_sample}
    \end{center}
    \caption{
        Magnitude and color distributions of synthetic stars.
        \textbf{Upper panel}: five-band magnitude distributions of the COSMOS
        stars (filled histograms) and  resampled stars (dashed lines).
        \textbf{Lower panel}: color-color distributions
        (left: $g-r$ v.s. $r-i$; right: $i-z$ v.s. $z-y$). 
        Filled-contours indicate COSMOS stars and open-contours indicate resampled stars.
        }
    \label{fig:star_sample}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

@@

%% ------------------------------------------------------------------------------------ %%
%% Fig: Magnitude v.s S/N for stars
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_psf_sn}
    \end{center}
    \caption{
        Relation between input magnitudes (\textbf{left}: $i$-band; \textbf{right}:
        $g$-band) of synthetic stars and the $\log (\mathrm{S}/\mathrm{N})$ measured 
        by \hscpipe{} PSF photometry.
        Filled-contours and open-contours show the distributions for
        stars in both the \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}. 
        Highly blended stars are highlighted using scatter plots.
        The gray dashed line marks $S/N = 5$ which is the detection threshold used 
        by \hscpipe{}.  
        Our 5$\sigma$ point source detection limit is ${\sim}26.5$ mag in $i$-band,
        however we do not reach these magnitudes with our current synthetic stellar 
        input catalog.
        }
    \label{fig:star_sn}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
%% Fig: Accuracy of Forced PSF Magnitudes
\begin{figure*}
    \begin{center}
        \includegraphics[width=16cm]{fig/synpipe_psf_mag}
    \end{center}
    \caption{
        Accuracy of the \texttt{hscpipe} PSF photometry for synthetic stars measured
        by the difference between input and output \forced{} PSF magnitudes.
        Plots [a, b, c, d, e] show the results for [$g$, $r$, $i$, $z$, $y$]-band, 
        respectively.
        The left panel in each plot shows the relation between input magnitude and
        magnitude difference.
        Filled and open contours are for the synthetic galaxies 
        from \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}.
        Highly blended objects are highlighted using scattered points.
        The long-dashed lines mark zero magnitude difference, while the pairs of
        dashed lines outline the running-median of PSF magnitude errors
        (including the uncertainties in aperture correction).
        The right panel in each plot shows the distributions of the magnitude 
        differences for objects in \texttt{goodSeeing} (filled) and \texttt{badSeeing}
        (solid line) \tracts{}.
        The dashed lines identify the distribution of highly blended objects.
        }
    \label{fig:psf_mag}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %%
%% Fig: Astrometric Calibration
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_astrometry}
    \end{center}
    \caption{
        Astrometric accuracy for synthetic stars (\textbf{left}) and galaxies
        (\textbf{right}). 
        We show the differences between the input R.A and Dec and the coordinates 
        measured on the \coadd{} images. 
        Filled-contours (filled histogram) and open-contours (solid-line histogram) are 
        for synthetic objects from \tracts{} with good and bad seeing conditions, 
        respectively.
        $\Delta\mathrm{R.A}=0$ and $\Delta\mathrm{Dec}=0$ are marked by dashed lines.     
        It shows that the initial astrometric calibration is already very accurate,  
        and it also suggests that \hscpipe{} can find the centroids of stars and 
        galaxies with precisions that are consistent with the astrometric calibration
        uncertainty under moderately different seeing conditions.
        }
    \label{fig:astrometry}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
%% Fig: Star-Galaxy Separation
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_star_galaxy}
    \end{center}
    \caption{Evaluation of the \hscpipe{} star--galaxy separation scheme. 
        Star--galaxy separation is based on the the magnitude difference between the 
        PSF and \cmodel{} photometry. 
        The plot on the \textbf{left} (a) corresponds to synthetic stars. 
        Filled-contours and filled histogram show distributions of correctly classified
        synthetic stars in the \texttt{goodSeeing} \tract{}.
        The scatter plot (dashed-line histogram) and open-contour (solid-line histogram)
        show distributions of synthetic stars that are misclassified as extended
        objects in \tracts{} with bad and good seeing conditions, respectively.
        The plot on the \textbf{right} (b) corresponds to synthetic galaxies.
        Filled-contours (filled histogram) and open-contours (solid-line histogram)
        are for galaxies from \texttt{goodSeeing} and \texttt{badSeeing} \tracts{},
        respectively.
        The scatter plot and dashed-line histogram highlight synthetic galaxies that 
        are misclassified as point sources.}
    \label{fig:sg}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
%% Fig: Relations between Blendedness and Photomertic Errors
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_blendedness_err}
    \end{center}
    \caption{
        Relation between the $\log_{10} (\mathrm{Blendedness})$ parameter
        and the photometric accuracy f synthetic stars (\textbf{upper row}, a and 
        b) and galaxies (\textbf{lower row}, c and d).
        \textbf{Left} columns (a and c) show the uncertainties in PSF and/or \cmodel{} 
        magnitudes. \textbf{Right} columns (b and d) show the uncertainties in 
        $(g-i)$ colors.
        Filled-contours and open-contours show results for \texttt{goodSeeing} and
        \texttt{badSeeing} \tracts{}, respectively.
        $\log_{10} (\mathrm{Blendedness}) = -1.0$ is marked using a vertical dashed 
        line.
        }
    \label{fig:blend}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
%% Fig: HSC cModel has problem recovering the size and shape of galaxies
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_galaxy_ba}
    \end{center}
    \caption{
        Accuracy of weighted axis ratio estimates for synthetic
        galaxies using \cmodel{} photometry.
        The \textbf{left} (a) plot shows the relation between the input $(b/a)$ and 
        the uncertainty in $(b/a)$.
        The \textbf{right} (b) plot shows the relation between input magnitude and 
        the undertainty in $(b/a)$.
        Open-contours are for the default test with \texttt{usePixelWeights=False}, and 
        filled-contours correspond to \texttt{usePixelWeights=True}.
        }
    \label{fig:galaxy_ba}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %%
% Table 1 : Magnitudes for PSF
\begin{table*}
    \begin{center}
    %% -------------------------------------------------------------------------------- %%
    \begin{tabular}{| c | c | c | ccccccc |}
    \hline
    Filter &   Seeing    &  Statistics & \multicolumn{7}{|c|}{Input Magnitudes (mag)} \\
    \cline{4-10}
           & FWHM ($$\asec) &             & 19.0 & 20.0 & 21.0 & 22.0 & 23.0 & 24.0 & 25.0 \\
    \hline
    $g$ & 0.45 & \smag{} & 0.016 & 0.017 & 0.019 & 0.023 & 0.029 & 0.043 & 0.078 \\
        &      & \mmag{}  & 0.008 & 0.009 & 0.009 & 0.009 & 0.008 & 0.007 & $\minus 0.003$ \\
        \cline{3-10}
        & 0.70 & \smag{} & 0.016 & 0.018 & 0.019 & 0.021 & 0.026 & 0.039 & 0.091 \\
        &      & \mmag{}  & 0.007 & 0.006 & 0.006 & 0.005 & 0.004 & 0.003 & $\minus 0.002$ \\
    \hline
    $r$ & 0.45 & \smag{} & 0.021 & 0.023 & 0.024 & 0.025 & 0.027 & 0.035 & 0.064 \\
        &      & \mmag{}  & 0.011 & 0.011 & 0.012 & 0.011 & 0.012 & 0.011 & 0.011 \\
        \cline{3-10}
        & 0.70 & \smag{} & 0.026 & 0.029 & 0.031 & 0.034 & 0.041 & 0.054 & 0.090 \\
        &      & \mmag{}  & 0.009 & 0.009 & 0.009 & 0.009 & 0.009 & 0.006 & 0.001 \\    
    \hline
    $i$ & 0.45 & \smag{} & 0.015 & 0.015 & 0.017 & 0.018 & 0.020 & 0.030 & 0.047 \\
        &      & \mmag{}  & 0.002 & 0.002 & 0.002 & 0.002 & 0.002 & 0.002 & 0.003 \\
        \cline{3-10}
        & 0.70 & \smag{} & 0.012 & 0.013 & 0.014 & 0.016 & 0.022 & 0.043 & 0.050 \\
        &      & \mmag{}  & 0.001 & 0.002 & 0.002 & 0.002 & 0.002 & 0.001 & $\minus 0.012$ \\    
    \hline
    $z$ & 0.45 & \smag{} & 0.011 & 0.013 & 0.014 & 0.016 & 0.025 & 0.053 & 0.094 \\
        &      & \mmag{}  & 0.002 & 0.002 & 0.002 & 0.003 & 0.003 & 0.005 & $\minus 0.001$ \\
        \cline{3-10}
        & 0.70 & \smag{} & 0.019 & 0.020 & 0.021 & 0.024 & 0.038 & 0.071 & 0.104 \\
        &      & \mmag{}  & 0.003 & 0.003 & 0.003 & 0.004 & 0.005 & 0.003 & $\minus 0.010$ \\    
    \hline
    $y$ & 0.45 & \smag{} & 0.017 & 0.017 & 0.021 & 0.033 & 0.074 & 0.138 & -- \\
        &      & \mmag{}  & 0.006 & 0.006 & 0.006 & 0.006 & 0.000 & $\minus 0.001$ & -- \\
        \cline{3-10}
        & 0.70 & \smag{} & 0.019 & 0.019 & 0.023 & 0.037 & 0.077 & 0.153 & -- \\
        &      & \mmag{}  & 0.007 & 0.008 & 0.008 & 0.006 & 0.003 & $\minus 0.034$ & -- \\    
    \hline  
    \end{tabular}
    %% -------------------------------------------------------------------------------- %%
    \end{center}
    \caption{
        Summary of precisions and accuracies of \forced{} PSF magnitudes in all 
        five bands and in both \texttt{goodSeeing} (FWHM$=0.45$\asec{}) and
        \texttt{badSeeing} (FWHM$=0.70$\asec{}) \tracts{} based on the statistics of 
        the difference between output \forced{} PSF magnitude and input 
        value ($\Delta\mathrm{mag}$) shown in Fig \ref{fig:psf_mag}.
        Here, the precision is described using the statistical uncertainties of 
        $\Delta\mathrm{mag}$ within a series of input magnitude bins (\smag{}). 
        The accuracy of PSF photometry in the same magnitude bin is described by the 
        mean value of $\Delta\mathrm{mag}$.
        }
        \label{tab:psfmag}
\end{table*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
% Table 2 : PSF Color
\begin{table*}
    \begin{center}
    %% -------------------------------------------------------------------------------- %%
    \begin{tabular}{| c | c | c | ccccccc |}
    \hline
    Filter &   Seeing       &  Statistics & \multicolumn{4}{|c|}{Input $i$ band Magnitudes (mag)} \\
    \cline{4-10}
           & FWHM ($$\asec) &             & 19.0 & 20.0 & 21.0 & 22.0 & 23.0 & 24.0 & 25.0 \\
    \hline
    $(g-i)$ & 0.45 & \scolor{} & 0.023 & 0.026 & 0.037 & 0.054 & 0.077 & 0.105 & 0.117 \\
            &      & \mcolor{}  & 0.008 & 0.007 & 0.005 & 0.003 & $\minus 0.002$ & $\minus 0.009$ & $\minus 0.035$ \\
            \cline{3-10}
            & 0.70 & \scolor{} & 0.021 & 0.025 & 0.033 & 0.051 & 0.075 & 0.105 & 0.137 \\
            &      & \mcolor{}  & 0.004 & 0.003 & 0.002 & 0.001 & $\minus 0.001$ & $\minus 0.002$ & 0.007 \\
    \hline
    $(i-y)$ & 0.45 & \scolor{} & 0.019 & 0.020 & 0.022 & 0.031 & 0.058 & 0.109 & 0.189 \\
            &      & \mcolor{}  & $\minus 0.004$ & $\minus 0.004$ & $\minus 0.004$ & $\minus 0.004$ & $\minus 0.002$ & 0.011 & 0.064 \\
            \cline{3-10}
            & 0.70 & \scolor{} & 0.019 & 0.020 & 0.021 & 0.031 & 0.057 & 0.123 & 0.221 \\
            &      & \mcolor{}  & $\minus 0.006$ & $\minus 0.006$ & $\minus 0.006$ & $\minus 0.005$ & $\minus 0.005$ & $\minus 0.002$ & $\minus 0.064$ \\    
    \hline  
    \end{tabular}
    %% -------------------------------------------------------------------------------- %%
    \end{center}
    \caption{
        Summary of precisions and accuracies of \forced{} PSF colors using $(g-i)$ and 
        $(i-y)$ colors and in both \texttt{goodSeeing} (FWHM$=0.45$\asec{}) and
        \texttt{badSeeing} (FWHM$=0.70$\asec{}) \tracts{} based on the statistics of 
        the difference between output \forced{} PSF color and input value 
        ($\Delta\mathrm{Color}$) shown in Fig \ref{fig:psf_color}.
        Here, we describe the precision and accuracy of PSF color measurements using 
        the statistical uncertainties and mean values of $\Delta\mathrm{Color}$ in 
        bins of input $i$ band magnitudes.
    }
        \label{tab:psfcolor}
\end{table*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
% Table 3 : Magnitudes for cModel
\begin{table*}
    \begin{center}
    %% -------------------------------------------------------------------------------- %%
    \begin{tabular}{| c | c | c | cccccc |}
    \hline
    Filter & Seeing & Statistics & \multicolumn{6}{|c|}{Input Magnitudes (mag)} \\
    \cline{4-9}
           & FWHM ($$\asec) &             & 20.0 & 21.0 & 22.0 & 23.0 & 24.0 & 25.0 \\
    \hline
    $g$ & 0.45 & \smag{} & 0.111 & 0.156 & 0.161 & 0.152 & 0.176 & 0.196 \\
        &      & \mmag{}  & $\minus 0.060$ & $\minus 0.036$ & $\minus 0.004$ & 0.021 & 0.009 & $\minus 0.005$ \\
        \cline{3-9}
        & 0.70 & \smag{} & 0.137 & 0.161 & 0.138 & 0.147 & 0.181 & 0.202 \\
        &      & \mmag{}  & 0.018 & $\minus 0.008$ & 0.029 & 0.040 & 0.028 & 0.012 \\
    \hline
    $r$ & 0.45 & \smag{} & 0.197 & 0.151 & 0.147 & 0.167 & 0.179 & 0.211  \\
        &      & \mmag{}  & $\minus0.036$ & $\minus 0.015$ & 0.033 & 0.033 & 0.017 & 0.012  \\
        \cline{3-9}
        & 0.70 & \smag{} & 0.167 & 0.119 & 0.142 & 0.168 & 0.189 & 0.232 \\
        &      & \mmag{}  & $\minus 0.024$ & 0.023 & 0.050 & 0.036 & 0.025 & 0.022 \\    
    \hline
    $i$ & 0.45 & \smag{} & 0.173 & 0.157 & 0.154 & 0.168 & 0.183 & 0.218 \\
        &      & \mmag{}  & $\minus 0.023$ & 0.008 & 0.004 & 0.017 & $\minus 0.001$ & $\minus 0.006$ \\
        \cline{3-9}
        & 0.70 & \smag{} & 0.154 & 0.157 & 0.153 & 0.174 & 0.193 & 0.246 \\
        &      & \mmag{}  & 0.017 & 0.043 & 0.040 & 0.021 & 0.003 & $\minus 0.013$ \\
    \hline
    $z$ & 0.45 & \smag{} & 0.171 & 0.176 & 0.165 & 0.182 & 0.201 & 0.241 \\
        &      & \mmag{}  & $\minus0.006$ & 0.042 & 0.038 & 0.018 & $\minus 0.002$ & $\minus 0.012$ \\
        \cline{3-9}
        & 0.70 & \smag{} & 0.168 & 0.155 & 0.167 & 0.185 & 0.222 & 0.278 \\
        &      & \mmag{}  & 0.027 & 0.046 & 0.045 & 0.028 & 0.009 & $\minus 0.034$ \\    
    \hline
    $y$ & 0.45 & \smag{} & 0.179 & 0.169 & 0.178 & 0.197 & 0.241 & 0.308 \\
        &      & \mmag{}  & 0.011 & 0.056 & 0.044 & 0.014 & $\minus 0.067$ & $\minus 0.244$ \\
        \cline{3-9}
        & 0.70 & \smag{} & 0.169 & 0.164 & 0.169 & 0.194 & 0.253 & 0.315 \\
        &      & \mmag{}  & 0.041 & 0.052 & 0.048 & 0.020 & $\minus 0.057$ & $\minus 0.299$ \\    
    \hline  
    \end{tabular}
    %% -------------------------------------------------------------------------------- %%
    \end{center}
    \caption{
        Summary of precisions and accuracies of \forced{} \cmodel{} magnitudes in all 
        five bands and in both \texttt{goodSeeing} (FWHM$=0.45$\asec{}) and
        \texttt{badSeeing} (FWHM$=0.70$\asec{}) \tracts{} based on the statistics of 
        the difference between output \forced{} \cmodel{} magnitude and input 
        value ($\Delta\mathrm{mag}$) shown in Fig \ref{fig:cmodel_mag}.
        Other details are the same with Table \ref{tab:psfmag}.}
        \label{tab:cmodelmag}
\end{table*}
%% ------------------------------------------------------------------------------------ %%
